Cloud Supercomputing with the ExaHyPE-Engine\\Master Thesis Kick-Off

### 2018-10-17 writing/slides/kick_off.tex
Improve slides using bold text.

  Gravitational force and pressure-gradient force are exactly balanced.

@@

\begin{frame}{The ADER-DG Approach\footfullcite{dumbser2008unified}}
  Solve hyperbolic conservation laws of the form
\begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q) = S(\bm{x}, t, Q)
\end{equation}
with $Q$ vector of conserved variables, $\bm{x}$ position, $t$ time,  $\nabla \cdot F(Q)$ divergence of flux and $S(\bm{x}, t, Q)$ source term.

Discontinous Galerkin (DG) divides domain into disjoint elements, approximates solutions by discontinous polynomials.
Elements are connected by solving the Riemann problem.

ADER-Approach uses space-time polynomials for time integration instead of Runge-Kutta procedures.

Implemented in the PDE-Framework ExaHyPe.
\end{frame}

@@

Flux:
\begin{equation}
  F(Q, \nabla Q) = 
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q)}  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q))} -
    \textcolor{orange}{\kappa \nabla T}
  \end{pmatrix}
\end{equation}

@@

Solution:
Change numerical flux (Riemann solver), time step size (CFL-Condition) and boundary conditions to allow diffusive terms\footfullcite{dumbser2010arbitrary}.

@@

  \begin{block}{Goals}
  \begin{itemize}
  \item Fix convergence
  \item Finite Volume Limiting\footfullcite{dumbser2016simple}
  \item Adaptive Grids
  \item Coupling of Navier-Stokes with other PDE (e.g.\ simple advection equation) by solving Riemann problem at boundary
  \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Current status of Convergence-Tests}
  \begin{figure}[h]
    \centering
   \includegraphics[width=0.8\textwidth]{{l2_error}}
    \caption{Mesh-Size vs $L_2$ error }
    \label{fig:l2-error}
  \end{figure}
\end{frame}

\begin{frame}{Summary}
  \begin{block}{Main Objectives}
  \begin{itemize}
  \item Dynamics of clouds can be simulated by Navier-Stokes equations.
  \item ADER-DG can be used to simulate Navier-Stokes equations.
  \item The ExaHyPE-Engine provides an efficient, scalable implementation of ADER-DG scheme. 
  \end{itemize}
  \end{block}

  \begin{block}{Bonus Objectives}
    \begin{itemize}
    \item All extensions to engine (diffusive fluxes, coupling) useful for other user of ExaHyPE
    \item First use of ExaHyPE-Engine for metrological simulations
    \end{itemize}

>>>>

  Gravitational force and pressure-gradient force are \textbf{exactly balanced}.

@@

\begin{frame}{The ADER-DG Approach\footfullcite{dumbser2008unified}}
  Solve \textbf{hyperbolic conservation laws} of the form
\begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q) = S(\bm{x}, t, Q)
\end{equation}
with $Q$ vector of conserved variables, $\bm{x}$ position, $t$ time,  $\nabla \cdot F(Q)$ divergence of flux and $S(\bm{x}, t, Q)$ source term.

\textbf{Discontinuous Galerkin} (\textsc{DG}) divides domain into disjoint elements, approximates solutions by piecewise-polynomials.
Elements are connected by solving the Riemann problem.

\textbf{ADER}-Approach uses space-time polynomials for time integration instead of Runge-Kutta procedures.

Implemented in the PDE-Framework \textbf{ExaHyPE}.
\end{frame}

@@

Flux:
\begin{equation}
  F(Q, \textcolor{orange}{\nabla Q}) = 
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q)}  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \textcolor{orange}{\stressT (Q, \nabla Q))} -
    \textcolor{orange}{\kappa \nabla T}
  \end{pmatrix}
\end{equation}

@@

\textbf{Solution}:
Modify numerical flux (Riemann solver), time step size (CFL-Condition) and boundary conditions to \textbf{allow diffusive terms}\footfullcite{dumbser2010arbitrary}.

@@

  \begin{block}{Goals}
  \begin{itemize}
  \item Fix convergence
  \item Adaptive Grids
  \item Finite Volume Limiting\footfullcite{dumbser2016simple}
  \item Coupling of Navier-Stokes with other PDE (e.g.\ simple advection equation) by solving Riemann problem at boundary
  \end{itemize}
  \end{block}
\end{frame}

% \begin{frame}{Current status of Convergence-Tests}
%   \begin{figure}[h]
%     \centering
%    \includegraphics[width=0.8\textwidth]{{l2_error}}
%     \caption{Mesh-Size vs $L_2$ error }
%     \label{fig:l2-error}
%   \end{figure}
% \end{frame}

\begin{frame}{Summary}
  \begin{block}{Main Objectives}
  \begin{itemize}
  \item \textbf{Navier-Stokes equations} can describe dynamics of clouds.
  \item \textbf{ADER-DG} can be used to discretize Navier-Stokes equations.
  \item The \textbf{ExaHyPE-Engine} provides an efficient, scalable implementation of ADER-DG scheme. 
  \end{itemize}
  \end{block}

  \begin{block}{Bonus Objectives}
    \begin{itemize}
    \item All extensions to engine (diffusive fluxes, coupling) useful for other user of ExaHyPE.
    \item First use of ExaHyPE-Engine for simulation of clouds.
    \end{itemize}
